\bf Forecast Reconciliation: A geometric view with new insights on bias correction.

### 2019-09-04 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Georges changes

	Multivariate time series following an aggregation structure arise in many sectors such as retail, energy, insurance, health and welfare and economics \citep{Karmy2019, Taieb2017, Almeida2016, JeoEtAl2019, Mahkya2017, LiTan2019, Shang2017}. Forecasts of these series should adhere to aggregation constraints to ensure aligned decision making. Earlier studies achieved this by only forecasting a single level of the hierarchy and then either aggregating in a bottom-up fashion \citep{Dunn1976} or disaggregating in a top-down fashion \citep{Gross1990, Athanasopoulos2009}.  For reviews of these approaches including a discussion of their advantages and disadvantages see \citet{Schwarzkopf1988, Kahn1998, Lapide1998, Fliedner2001}.

	In contrast to these methods, \cite{Hyndman2011} proposed forecasting all series in the hierarchy, referring to these as {\em base} forecasts.  Since base forecasts were produced independently they were not guaranteed to adhere to aggregation constraints and could thus be improved via further adjustment.  A framework was proposed whereby the base forecasts were assumed to follow a regression model.  The predicted values from this model were guaranteed to adhere to the linear constraints by construction and could thus be used as a new set of forecasts.  This approach and later modifications have subsequently been shown to outperform bottom-up and top-down approaches in a variety of empirical settings \citep{Hyndman2016, Athanasopoulos2009, Shang2017}.

	Some theoretical insight into the performance of forecast reconciliation methods has been provided by \cite{VanErven2015a} and \cite{WicEtAl2019}.  Both papers provide a proof that reconciliation is guaranteed to improve base forecasts.  The latter paper also proposes a particular version of reconciliation known as the Minimum Trace (MinT) method.  This is optimal in the sense of minimising the trace of reconciled forecast error covariance matrix under the assumption that base forecasts are unbiased.

@@

    Forecasting a single level of the hierarchy did not, however echo common practice within many industries.\todo{might need refs}  In many organisations different departments or `silos' each produced their own forecasts, often with their own information sets and judgemental adjustments.  This approach does have several advantages over only forecasting a single level.  First, there is no loss of information since all levels and series are modelled.  Second, modelling higher level series often identifies features such as trend and seasonality that cannot be detected in noisy disaggregate data.  However, when forecasts are produced independently at all levels, forecasts are likely to be incoherent.\footnote{There are some special cases of using simple approaches such as na\"{i}ve, which extrapolate the coherent nature of the data to the forecasts.} This problem of incoherent forecasts cannot in general be solved by multivariate modelling either.  Instead, the solution is to make an ex post adjustment that ensures coherence, a process known as {\em forecast reconciliation}

>>>>

	Multivariate time series following an aggregation structure arise in many sectors such as retail, energy, insurance, health and welfare and economics \citep[see for example][]{KarMal2019, Taieb2017, NysEtAl2019, AlmVan2016, JeoEtAl2019, Mahkya2017, LiTan2019, Shang2017, AthEtAl2019_MacroBook}. Forecasts of these series should adhere to aggregation constraints to ensure aligned decision making. Earlier studies achieved this by only forecasting a single level of the hierarchy and then either aggregating in a bottom-up fashion \citep{Dunn1976} or disaggregating in a top-down fashion \citep{Gross1990, Athanasopoulos2009}.  For reviews of these approaches including a discussion of their advantages and disadvantages see \citet{Schwarzkopf1988, Kahn1998, Lapide1998, Fliedner2001}.

	In contrast to these methods, \cite{Hyndman2011} proposed forecasting all series in the hierarchy, referring to these as {\em base} forecasts.  Since base forecasts were produced independently they were not guaranteed to adhere to aggregation constraints and could thus be improved via further adjustment.  A framework was proposed whereby the base forecasts were assumed to follow a regression model.  The predicted values from this model were guaranteed to adhere to the linear constraints by construction and could thus be used as a new set of forecasts.  This approach and later modifications have subsequently been shown to outperform bottom-up and top-down approaches in a variety of empirical settings \citep[see for example][among others]{Athanasopoulos2009, AthEtAl2017, WicEtAl2019}.	Some theoretical insight into the performance of forecast reconciliation methods has been provided by \cite{VanErven2015a} and \cite{WicEtAl2019}.  Both papers provide a proof that reconciliation is guaranteed to improve base forecasts.  The latter paper also proposes a particular version of reconciliation known as the Minimum Trace (MinT) method.  This is optimal in the sense of minimising the trace of reconciled forecast error covariance matrix under the assumption that base forecasts are unbiased.

@@

    Forecasting a single level of the hierarchy did not, however echo common practice within many industries. In many organisations different departments or `silos' each produced their own forecasts, often with their own information sets and judgemental adjustments. \footnote{\cite{Cha2013} discusses silos and the importance of information and data sharing across an organisation.}  This approach does have several advantages over only forecasting a single level.  First, there is no loss of information since all levels and series are modelled.  Second, modelling higher level series often identifies features such as trend and seasonality that cannot be detected in noisy disaggregate data.  However, when forecasts are produced independently at all levels, forecasts are likely to be incoherent.\footnote{There are some special cases of using simple approaches such as na\"{i}ve, which extrapolate the coherent nature of the data to the forecasts.} This problem of incoherent forecasts cannot in general be solved by multivariate modelling either.  Instead, the solution is to make an ex post adjustment that ensures coherence, a process known as {\em forecast reconciliation}
